### 2013-02-18 au_topology_seminar_talk_2013_02_18.tex
Final touches to seminar talk feb 2013

\centerline{\bf An Example of Gruenhage's Compact-Point Game for which $K$ has }
\centerline{\bf a winning strategy, but no winning $k$-tactical strategy}

@@

\begin{theorem}\label{basic_x}
There exists a compact, zero-dimensional topological space $X$ which has a point-countable cover $\mathcal{U} = \{U_c : c \in 2^\omega\}$ which is not the union of countably-many point-finite collections.
\end{theorem}

\begin{proof}
Take a zero-dimensional Corson compact $Y$ of weight $2^\omega$, which is not Eberlein compact. It follows by \cite{G1} that $Y^2 \setminus \Delta = \{(y_1,y_2): y_1,y_2 \in Y, y_1\not=y_2\}$ is metalindelof, but not $\sigma$-metacompact. So every cover has a point-countable refinement of cardinality $2^\omega$, but no open refinement composed of the union of countably-many point-finite collections.
\end{proof}

\begin{example}
Using the $X$ from Theorem \ref{basic_x}, let \[\mathbb{X} = (X \times 2^{<\omega}) \cup 2^\omega\] compose a disjoint union of $2^{<\omega}$ copies of $X$ along with a discrete copy of the Cantor Set $2^\omega$, and add open neighborhoods of the form: 
  \[
    B_c = c \cup (U_c \times \{c\rest n : n < \omega\})
  \]
as seen in Figure \ref{fig:cantor_tree}.
\end{example}

@@

\begin{definition}
Let $S\in[2^\omega]^{<\omega}$ and $m<\omega$. Define 
  \[
    K_S = \bigcup_{c \in S} B_c
  \] 
  \[ 
    A = \{z^\frown \<1\> : z \in 1^{<\omega}\}
  \] 
  \[ 
    K^*_S = K_S \setminus (X \times A)
  \] 
  \[
    L_m = X \times 2^{<m}
  \] 
and observe that every compact set is dominated by $K^*_S \cup L_m$ for some $S,m$.

@@

@@

This is a winning strategy because each point $\<x_i,s_i\>$ played by $P$ cannot be a part of a sequence converging to some $c^{x_i}_n$, since a $K_{\{c^{x_i}_0,\dots,c^{x_i}_n\}} \supseteq B_{c^{x_i}_n}$ was forbidden during round $n$.
\end{proof}

@@

\begin{proof}
This is actually a corollary of Gruenhage's theorem in \cite{G2} by proving $\mathbb{X}$ is not metacompact. The following is a direct game-theoretic proof.

@@

Recall that $\mathcal{U}$ is not the union of the countably-many point-finite collections, and 
  \[
    \mathcal{U} = \bigcup_{n<\omega} \{U_c : f(c) = n\}
  \]
so we may find choose $n$ where $\mathcal{U}_n = \{U_c : f(c) = n\}$ is not point-finite. Fix $x$ so that $x$ belongs to each of $\{U_{c_0},U_{c_1},\dots\} \subseteq \mathcal{U}_n$.

For each $c_i$, $\sigma'(x,f(c_i))=\sigma'(x,n)$ covers $c_i$. Thus $\sigma'(x,n) \supseteq \{c_0,c_1,\dots\}$ is not compact, a contradiction.
\end{proof}

@@

Since $\<x_{i+1},s_{i+1}\>$ was legal against $\tau$, it avoided
  \[
    K^*_{S(x_h,x',m(x_h,x',|s_h|)+1)} = 
    K^*_{S(x_h,x',\max(|s_h|,|{z_{m(x_h,x',|s_h|)}}^\frown\<1\>|))}
  \]
for $h\leq i$. And when $h<i$, we see it avoids:
  \[
    K^*_{S(x_{h+1},x',\max(|s_{h+1}|,|{z_{m(x_h,x',|s_h|)}}^\frown\<1\>|))} =
    K^*_{S(x_{h+1},x',|s_{h+1}|)}
  \]
  \[
    \subseteq
    K^*_{S(x_{h+1},x',m(x_{h+1},x',|s_{h+1}|)+1)}
  \]

@@

Since $\<x_{i+1},s_{i+1}\>$ was legal against $\tau$, it avoided
  \[
    K^*_{S(x_h,x',\dots,x',M^{k-1}(x_h,|s_h|)+1)} 
  \]
  \[
    = 
    K^*_{S(x_h,x',\dots,x',\max(|s_h|,|{z_{M^{0}(x_h,|s_h|)}}^\frown\<1\>|,\dots,|{z_{M^{k-1}(x_h,|s_h|)}}^\frown\<1\>|))}
  \]
for $h\leq i$. And when $h<i$, we see it avoids both:
  \[
    K^*_{S(x_{h+1},x',\dots,x',\max(|s_{h+1}|,|{z_{M^0(x_{h+1},|s_{h+1}|)}}^\frown\<1\>|,\dots,|{z_{M^{j-1}(x_{h+1},|s_{h+1}|)}}^\frown\<1\>|,|{z_{M^{j}(x_{h},|s_{h}|)}}^\frown\<1\>|,\dots,|{z_{M^{k}(x_{h},|s_{h}|)}}^\frown\<1\>|))} 
  \]
  \[
    =
    K^*_{S(x_{h+1},x',\dots,x',|{z_{M^{j-1}(x_{h+1},|s_{h+1}|)}}^\frown\<1\>|)}
  \]
  \[
    =
    K^*_{S(x_{h+1},x',\dots,x',M^{j-1}(x_{h+1},|s_{h+1}|)+1)}
  \]
  \[
    \subseteq
    K^*_{S(x_{h+1},x',\dots,x',M^{k-1}(x_{h+1},|s_{h+1}|)+1)}
  \]
and:
  \[
    K^*_{S(x_{h+1},x',\dots,x',\max(|s_{h+1}|,|{z_{M^0(x_{h},|s_{h}|)}}^\frown\<1\>|,\dots,|{z_{M^{k}(x_{h},|s_{h}|)}}^\frown\<1\>|))} 
  \]
  \[
    =
    K^*_{S(x_{h+1},x',\dots,x',|s_{k+1}|)}
  \]
  \[
    \subseteq
    K^*_{S(x_{h+1},x',\dots,x',M^{k-1}(x_{h+1},|s_{h+1}|)+1)}
  \]

@@

@@

\bibitem{Watson}
  S. Watson,
  \emph{Locally compact normal meta-Lindelöf spaces may not be paracompact: 
  an application of uniformization and Suslin lines}. 
  Proc. Amer. Math. Soc. 98 (1986), no. 4, 676–680.

>>>>

\centerline{\bf An Example of Gruenhage's Compact-Point Game for which $K$ has }
\centerline{\bf a winning strategy, but no winning $k$-Markov strategy}

@@

\begin{theorem}\label{basic_x}
There exists a compact, zero-dimensional topological space $X$ which has a point-countable cover $\mathcal{U} = \{U_c : c \in 2^\omega\}$ of clopen sets which is not the union of countably-many point-finite collections.
\end{theorem}

\begin{proof}
Take a zero-dimensional Corson compact $Y$ of weight $2^\omega$, which is not Eberlein compact. It follows by \cite{G1} that $Y^2 \setminus \Delta = \{(y_1,y_2): y_1,y_2 \in Y, y_1\not=y_2\}$ is metalindel\"of, but not $\sigma$-metacompact.

Let $X = Y^2$, and let $\mathcal{V}$ be an open cover of $X$ by $2^\omega$ clopen sets. Since $Y^2 \setminus \Delta$ is metalindel\"of and $\Delta$ is compact, let $\mathcal{V}'$ be a refinement of $\mathcal{U}$ such that it is a point-countable cover of $Y^2 \setminus \Delta$, and let $\mathcal{V}''$ be a refinement of $\mathcal{U}$ such that it is finite cover of $\Delta$. Then $\mathcal{U} = \mathcal{V}'\cup\mathcal{V}''$ is point-countable on $Y^2$, and if it was the union of countably-many point-finite collections, so would $\mathcal{V}'$ (making $Y^2\setminus \Delta$ $\sigma$-metacompact, contradiction).
\end{proof}

\begin{definition}
Using the $X$ from Theorem \ref{basic_x}, let \[\mathbb{X} = (X \times 2^{<\omega}) \cup 2^\omega\] compose a topological sum of $2^{<\omega}$ copies of $X$ along with a discrete copy of the Cantor Set $2^\omega$, and add open (in fact, compact) neighborhoods of the form: 
  \[
    B_c = c \cup (U_c \times \{c\rest n : n < \omega\})
  \]
as seen in Figure \ref{fig:cantor_tree}.
\end{definition}

@@

\begin{definition}
Let $S\in[2^\omega]^{<\omega}$ and $m<\omega$. Define 
  \[
    K_S = \bigcup_{c \in S} B_c
  \] 
  \[ 
    A = \{z^\frown \<1\> : z \in 1^{<\omega}\}
  \] 
  \[ 
    K^*_S = K_S \setminus (X \times A)
  \] 
  \[
    L_m = X \times 2^{<m}
  \] 
and observe that every compact set is dominated by the compact set $K^*_S \cup L_m$ for some $S,m$.

@@

\begin{definition}
We say $I \win G$ if Player $I$ has a winning strategy in the game $G$.

We say $I \tactwin G$ (resp. $I \ktactwin{k} G$) if Player $I$ has a winning tactical (resp. $k$-tactical) strategy in the game $G$, a strategy depending on only the ($k$) most recent move(s) of the opponent.

We say $I \markwin G$ (resp. $I \kmarkwin{k} G$) if Player $I$ has a winning Markov (resp. $k$-Markov) strategy in the game $G$, a strategy depending on only the ($k$) most recent move(s) of the opponent and the current round number.
\end{definition}

@@

This is a winning strategy because each move $\<x_i,s_i\>$ by $P$ cannot be a part of a subsequence of the play converging to any $c^{x_i}_n$, since $K_{\{c^{x_i}_0,\dots,c^{x_i}_n\}} \supseteq B_{c^{x_i}_n}$ was forbidden during round $n$.
\end{proof}

@@

\begin{proof}
This is actually a corollary of Gruenhage's theorem in \cite{G2}: $\mathbb{X}$ is locally compact (each point is either in some $X$ or in some $B_c$) but not metacompact (any cover of $2^\omega$ necessarily will have infinite overlap at some $X \times \{s\}$). However, we proceed with a direct game-theoretic proof.

@@

Recall that $\mathcal{U}$ is not the union of the countably-many point-finite collections, and 
  \[
    \mathcal{U} = \bigcup_{n<\omega} \{U_c : f(c) = n\}
  \]
so we may choose $n$ where $\mathcal{U}_n = \{U_c : f(c) = n\}$ is not point-finite. Fix $x$ so that $x$ belongs to each of $\{U_{c_0},U_{c_1},\dots\} \subseteq \mathcal{U}_n$.

For each $c_i$, $\sigma'(x,f(c_i))=\sigma'(x,n)$ covers $c_i$. Thus $\sigma'(x,n) \supseteq \{c_0,c_1,\dots\}$ is a compact set covering a closed discrete subset, a contradiction.
\end{proof}

@@

Since $\<x_{i+1},s_{i+1}\>$ was legal against $\tau$, for $h\leq i$ it avoided
  \[
    K^*_{S(x_h,x',m(x_h,x',|s_h|)+1)} = 
    K^*_{S(x_h,x',\max(|s_h|,|{z_{m(x_h,x',|s_h|)}}^\frown\<1\>|))}
  \]
and when $h<i$, we see it avoids:
  \[
    K^*_{S(x_{h+1},x',\max(|s_{h+1}|,|{z_{m(x_h,x',|s_h|)}}^\frown\<1\>|))} =
    K^*_{S(x_{h+1},x',|s_{h+1}|)}
  \]
  \[
    \subseteq
    K^*_{S(x_{h+1},x',m(x_{h+1},x',|s_{h+1}|)+1)}
  \]

@@

Since $\<x_{i+1},s_{i+1}\>$ was legal against $\tau$, for $h\leq i$ it avoided
  \[
    K^*_{S(x_h,x',\dots,x',M^{k-1}(x_h,|s_h|)+1)} 
  \]
  \[
    = 
    K^*_{S(x_h,x',\dots,x',\max(|s_h|,|{z_{M^{0}(x_h,|s_h|)}}^\frown\<1\>|,\dots,|{z_{M^{k-1}(x_h,|s_h|)}}^\frown\<1\>|))}
  \]
and when $h<i$, we see it avoids both:
  \[
    K^*_{S(x_{h+1},x',\dots,x',\max(|s_{h+1}|,|{z_{M^0(x_{h+1},|s_{h+1}|)}}^\frown\<1\>|,\dots,|{z_{M^{j-1}(x_{h+1},|s_{h+1}|)}}^\frown\<1\>|,|{z_{M^{j}(x_{h},|s_{h}|)}}^\frown\<1\>|,\dots,|{z_{M^{k}(x_{h},|s_{h}|)}}^\frown\<1\>|))} 
  \]
  \[
    =
    K^*_{S(x_{h+1},x',\dots,x',|{z_{M^{j-1}(x_{h+1},|s_{h+1}|)}}^\frown\<1\>|)}
  \]
  \[
    =
    K^*_{S(x_{h+1},x',\dots,x',M^{j-1}(x_{h+1},|s_{h+1}|)+1)}
  \]
  \[
    \subseteq
    K^*_{S(x_{h+1},x',\dots,x',M^{k-1}(x_{h+1},|s_{h+1}|)+1)}
  \]
and:
  \[
    K^*_{S(x_{h+1},x',\dots,x',\max(|s_{h+1}|,|{z_{M^0(x_{h},|s_{h}|)}}^\frown\<1\>|,\dots,|{z_{M^{k}(x_{h},|s_{h}|)}}^\frown\<1\>|))} 
  \]
  \[
    =
    K^*_{S(x_{h+1},x',\dots,x',|s_{k+1}|)}
  \]
  \[
    \subseteq
    K^*_{S(x_{h+1},x',\dots,x',M^{k-1}(x_{h+1},|s_{h+1}|)+1)}
  \]

@@

\begin{corollary}
$K\not\kmarkwin{k}\lfkpgame{\mathbb{X}}$.
\end{corollary}

\begin{proof}
Let $\sigma(\<x_0,s_0\>,\dots,\<x_{k-1},s_{k-1}\>,n)$ be a winning $k$-Markov strategy for $K$ increasing on $n$. We define a $k$-tactical strategy
  \[
    \tau(\<x_0,s_0\>,\dots,\<x_{k-1},s_{k-1}\>) = \sigma(\<x_0,s_0\>,\dots,\<x_{k-1},s_{k-1}\>,\max_{i<k}(|s_i|)) \cup L_{\max_{i<k}(|s_i|)+1}
  \]
and observe that since for any legal play of the game, the round number $n \leq \max_{i<k}(|s_i|)$, we know $\tau$ always yields supersets of $\sigma$, and is thus also a winning strategy, contradiction.
\end{proof}

@@

\bibitem{Watson}
  S. Watson,
  \emph{Locally compact normal meta-Lindel\"of spaces may not be paracompact: 
  an application of uniformization and Suslin lines}. 
  Proc. Amer. Math. Soc. 98 (1986), no. 4, 676–680.
